\sick, the spectroscopic inference crank

### 2014-08-28 document/manuscript.tex
Fixed mistake in variance of Eq. 11, and changed font for 'inferred' subscript

\begin{multline}
p_{outlier}\left(F_i|\lambda_i,\sigma_i,\bm{\kappa},V_{o},P_o\right) = \dots \\
  \frac{1}{\sqrt{2\pi\left(s_{i}^2 + V_{o}^2\right)}} \exp\left(-\frac{[F_i - C_i]^2}{2\left[s_{i}^2 + V_{o}^2\right]}\right)
\end{multline}

@@

For this example 1000 draws were made during the random scattering stage, and 
optimisation was performed using the default options. One hundred walkers 
explored the parameter space for 1000 steps, before another 200 steps were used 
to sample the posterior. The posterior distributions for stellar parameters is 
shown in Figure \ref{fig:solar}. The currently accepted stellar parameters for 
the Sun are $T_{\rm eff} = 5777$\,K, $\log{g} = 4.445$, [Fe/H] = 0, and 
[$\alpha$/Fe] = 0. The inferred parameters agree excellently with the accepted 
values for effective temperature and surface gravity: 
$T_{{\rm eff},inferred} = 5770^{+20}_{-14}$, and $\log{g}_{inferred} = 4.40^{+0.06}_{-0.05}$. 
The agreement is less pleasing for $\alpha$-element enhancement, and worse for 
mean metallicity: [$\alpha$/Fe]$_{inferred} = -0.03^{+0.01}_{-0.01}$, and 
[Fe/H]$_{inferred} = -0.07^{+0.01}_{-0.01}$.

>>>>

\begin{multline}
p_{outlier}\left(F_i|\lambda_i,\sigma_i,\bm{\kappa},V_{o},P_o\right) = \dots \\
  \frac{1}{\sqrt{2\pi\left(s_{i}^2 + V_{o}\right)}} \exp\left(-\frac{[F_i - C_i]^2}{2\left[s_{i}^2 + V_{o}\right]}\right)
\end{multline}

@@

For this example 1000 draws were made during the random scattering stage, and 
optimisation was performed using the default options. One hundred walkers 
explored the parameter space for 1000 steps, before another 200 steps were used 
to sample the posterior. The posterior distributions for stellar parameters is 
shown in Figure \ref{fig:solar}. The currently accepted stellar parameters for 
the Sun are $T_{\rm eff} = 5777$\,K, $\log{g} = 4.445$, [Fe/H] = 0, and 
[$\alpha$/Fe] = 0. The inferred parameters agree excellently with the accepted 
values for effective temperature and surface gravity: 
$T_{{\rm eff},{\rm inferred}} = 5770^{+20}_{-14}$, and $\log{g}_{\rm inferred} = 4.40^{+0.06}_{-0.05}$. 
The agreement is less pleasing for $\alpha$-element enhancement, and worse for 
mean metallicity: [$\alpha$/Fe]$_{\rm inferred} = -0.03^{+0.01}_{-0.01}$, and 
[Fe/H]$_{\rm inferred} = -0.07^{+0.01}_{-0.01}$.
